---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covideu

<!-- badges: start -->
[![R build status](https://github.com/etc5523-2020/r-package-assessment-jlee0179/workflows/R-CMD-check/badge.svg)](https://github.com/etc5523-2020/r-package-assessment-jlee0179/actions)
<!-- badges: end -->

The goal of covideu is to provide the main dataset used to create COVID-19 in EU app, along with several datasets that had been processed through data wrangling. In addition, three functions are developed to enable simpler and easier coding process within App.R.

## Installation

<!-- You can install the released version of covideu from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("covideu") -->
<!-- ``` -->

The development version can be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-jlee0179")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(covideu)
library(tibble)
owid
```
