---
title: "App Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{App Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(covideu)
```

### Launching the app
Within `covideu` package, a function called `launch_app()` is designed for launching the shiny app. This can be easily done by simply typing `launch_app()` in the console, without any argument.

### What the app does
The main role of "COVID-19 in EU" is to observe how Covid-19 has been affecting the people's lives in the European Union (EU) member countries. It gives the opportunity for users to view the pandemic condition through both short term and long term perspectives. The bar graph serves to enable comparisons to be made for the short term where by inputing a date and one or more countries, the daily numbers of cases and deaths will be immediately displayed. On the other hand, the trend of cumulative cases and deaths numbers is presented through the line graph below. It seems to be indirectly explaining whether the pandemic has been well-controlled or not over time through upward and downward sloping patterns. Lastly, the numbers in the table summarises the condition monthly, taking into account total cases and deaths numbers, population and case fatality rate, etc. Thus, users can interpret the condition by themselves numerically.

### Guideline for use
The input required for each graph or table is placed next to it in the left sidebar and is separated with adequate spaces. In specific, date and single or multiple countries are the required elements for the bar graph, the duration and country drop down menu for the line graph and finally the date or duration slider for the table. The output will change according to different input.